Software Citation Principles

### 2016-02-18 sc-principles/software-citation-principles.tex
adding an Arfon-note command and using it

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}

@@

With close to 50 working group partipants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants with the life sciences, astrophysics and geosciences being particularly well-represented in the submitted
resources.

@@

NOTE: Should mention that a number of communities have already focussed their attention on issues around data citation and while
this isn't exactly the same there are many similarities (what is different exactly?).

>>>>

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}}

@@

With close to 50 working group participants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants with the life sciences, astrophysics and geosciences being particularly well-represented in the submitted
resources.

@@

\asnote{Should mention that a number of communities have already focussed their attention on issues around data citation and while
this isn't exactly the same there are many similarities (what is different exactly?).}
